\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[margin=1in]{geometry}
    \usepackage{fontawesome}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-50pt}

    

%==== Profile ====%
\vspace*{-12pt}
\begin{center}
	{\Huge \scshape {Kondasamy Jayaraman}}\\
	\vspace{1mm}
	Bangkok, Thailand $\cdot$ 
	\faEnvelope \hspace{.5mm} \href{mailto:kondasamy@outlook.com}{kondasamy@outlook.com} $\cdot$ \faMobile \hspace{.5mm} +66-62545-3233 / +91-90034-94498
	
	\faGithub \hspace{.5mm} \href{https://github.com/Kondasamy}{GitHub} $\cdot$
	\faLinkedin \hspace{.5mm} \href{https://www.linkedin.com/in/kondasamy/}{LinkedIn} $\cdot$
	\faStackOverflow \hspace{.5mm} \href{https://stackoverflow.com/users/2094099/kondasamy-jayaraman}{Stack Overflow} $\cdot$
	\faMedium \hspace{.5mm} \href{https://medium.com/@kondasamy}{Medium}
	\faSkype \hspace{.5mm} \href{https://join.skype.com/invite/n0IMYwGkGwQ1}{Skype}\\
\end{center}

%==== Experience ====%
\header{WORK EXPERIENCE}
\vspace{1mm}

\textbf{Agoda [Booking Holdings Inc.,]} \hfill Bangkok, Thailand\\
\textit{Senior Software Dev. Engineer in Test (SDET) \textbar{} Data platform team} \hfill Jan 2019 | Present\\
\vspace{-1.5mm}
\begin{itemize} \itemsep 1pt
	\item Establish quality engineering and CI/ CD practices in Hadoop BigData environment.
	\item Code and maintain Scala based Unit and Integration tests.
\end{itemize}

\textbf{redBus [MakeMyTrip - Goibibo Group]} \hfill Bengaluru, India\\
\textit{Lead Software Dev. Engineer in Test (SDET) \textbar{} Inventory platform team} \hfill Oct 2018 | Dec 2018\\
\vspace{-1.5mm}
\begin{itemize} \itemsep 1pt
	\item Mentored and led efforts on automation framework development and test suite preparation.
\end{itemize}

\textbf{redBus [MakeMyTrip - Goibibo Group]} \hfill Bengaluru, India\\
\textit{Senior Software Dev. Engineer in Test (SDET) \textbar{} Inventory platform team} \hfill Mar 2017 | Sep 2018\\
\vspace{-1.5mm}
\begin{itemize} \itemsep 1pt
	\item Worked with Product \& Development teams to understand the business needs and identify the quality requirements and test automation goals.
	\item Supported Continuous Integration efforts, set up test automation tooling \& infrastructure and worked with developers to build and maintain it.
\end{itemize}

\textbf{Scientific Games Corporation} \hfill Bengaluru, India\\
\textit{Test Automation Engineer \textbar{} Back-end API team - Atlantic Lottery} \hfill Apr 2016 | Mar 2017\\
\vspace{-1.5mm}
\begin{itemize} \itemsep 1pt
	\item Performance tested the core back-end systems (microservices) and involved in strategic discussions on application performance tuning.
	\item Actively contributed to the tech strategy with insights on test automation and software quality.
\end{itemize}

\textbf{Cognizant Technology Solutions [Client: LexisNexis]} \hfill Coimbatore, India\\
\textit{Test Automation Engineer \textbar{} Back-end API team - Lexis Advance} \hfill Jul 2012 | Apr 2016\\
\vspace{-1.5mm}
\begin{itemize} \itemsep 1pt
	\item Problem solver and Responsible for test automation and regression test suite preparation for Service Oriented Architecture (SOA) applications. 
\end{itemize}

\header{SKILLS}
\begin{tabular}{ l l }
	Programming languages:      & Python, JavaScript, Groovy, Scala, Java, C\#                                            \\
	Databases:                  & MySQL, Postgres, MongoDB, Redis, Elastic Search         \\
	BigData tooling:                  & Cassandra, RedShift, Hadoop, Hive, Impala, Spark, Hue         \\
	Testing tools/ library:     & SoapUI, Ready API, Cypress, Selenium, UFT, CA DevTest             \\
	Application monitoring:     & New relic, Grafana, Kibana, Sentry, AWS Cloudwatch                \\
	Test automation frameworks: & Robot framework, SoapUI Hybrid framework, Cucumber (BDD)          \\
	Security testing tools:     & OWASP Zap, OWTF, BurpSuite                                        \\
	Load testing tools:         & JMeter, Gatling, Locust, LoadUI                                   \\
	DevOps:                     & TeamCity, Jenkins, Docker, Amazon web services, Azure \\
\end{tabular}
\vspace{2mm}

\header{INDEPENDENT PROJECTS}
{\textbf{SoapUI Plugin}} {\sl Groovy, Java, Gradle} \hfill https://github.com/Kondasamy/soapui-plugin-file-export\\
Automated test reports and logs generator for SoapUI and Ready API test runs.\\
\vspace*{2mm}
{\textbf{Automated Code Coverage}} {\sl VS Instrumentation, Jenkins} \\
CI framework to execute automated code coverage for .Net (C\#) projects and report generation.\\
\vspace*{2mm}

\header{AWARDS}
\textbf{Trailblazer award} \hfill \textit{redBus}\\
Recognized for implementing unit testing approach along with integration tests. \hfill \textit{Q1 2017 - 18}\\
\vspace*{1mm}
\textbf{Star of the month (Spot bonus)} \hfill \textit{Scientific Games}\\
Awarded for developing web services testing framework from the scratch. \hfill \textit{July 2016}\\
\vspace*{1mm}
\textbf{QEA Pride of the year} \hfill \textit{Cognizant Technology Solutions}\\
Recognized for implementing wiki portal and tech forum for internal team knowledge share. \hfill \textit{2015}\\
\vspace*{1mm}
\textbf{Idea champion of the year} \hfill \textit{Cognizant Innovation Group}\\
Awarded for ideating and managing innovation metrics for entire LexisNexis account. \hfill \textit{2014 \& 2015}\\
\vspace*{1mm}
\textbf{SmartBear Community Topper} \hfill \textit{SmartBear}\\
Been a problem solver for SoapUI community and topped the chart twice. \hfill \textit{Oct \& Nov 2015}\\
\vspace*{1mm}

%==== Education ====%
\header{EDUCATION}
\textbf{PSG College of Technology \textbar{} Anna University}\hfill Coimbatore, India\\
B.Sc Information Technology \textit{CGPA: 9.43/ 10} \hfill Jun 2009 - May 2012\\
\vspace*{-12pt}
\end{document}
